### 2022-03-08 paper/fse22/approach.tex
approach

\subsection{production differentiation phase}
Given the seed parse tree and reference \pcfg, \Model suggests
structural expansion candidates.

>>>>

\subsection{production differentiation phase}
\input{code/prod_diff_pseudocode}

Given the seed parse tree and reference \pcfg, production
differentiation phase suggests structural expansion candidates on the
seed input. this phase aims to analyze which structural components and
where they can be added into the seed structure for its expansion. To
do so, we explore reference production rules comparing it with each
production rule used in seed input. This results in the phase
described in Algorithm~\ref{code:ProdDiffAlg}. For each production
rule in seed inputs ($seed\_prod$), it searches production rules in
reference ($ref\_prod$) which it has same non-terminal on the
left-hand side ($seed\_prod.lhs==ref\_prod.lhs$) and superset of
right-hand side of the seed production rule ($seed\_prod.rhs \subset
ref\_prod.rhs$).  As we assume that the reference \cfg is built from
real world data distribution, the elements in the complement set
($ref\_prod.rhs - seed\_prod.rhs$) become an expansion candidate which
can be expanded from the $seed\_prod.rhs$ found in real world. In
addition, the measure of how consistent the production rule is with
the given seed structure is given in its probability of the reference
production rule ($ref\_prob$) multiplied by that of parents of
$seed\_prod$. The expansion candidate consists of terminal or
nonterminal symbols. When there is a phrase-level or clause-level
nonterminal symbol, \eg noun phrase, it needs to be expanded and
replaced with word-level nonterminal or terminal symbols to generate
the expansion candidate. The number of feasible replacement is
unbounded because of its high degree of freedom. Therefore, in this
work, we focus on the expansion candidate with only the word-level
nonterminal or terminal symbols for the effectiveness of \Model.
